\section{Assumptions}

\textbf{Assumption 1: (Data correctness \& structure)}
The Excel file \texttt{2026\_MCM\_Problem\_C\_Data.csv} is treated as the single source of truth. We assume judge score columns (when present) are recorded correctly, and the \texttt{results} field correctly indicates the eliminated week in the format ``Eliminated Week \{w\}''.

\textbf{Assumption 2: (Active roster definition)}
A couple is considered \emph{active} in a given week if they have not been eliminated before that week. Weeks where the eliminated couple cannot be uniquely identified from the data are excluded from inference and downstream comparisons.

\textbf{Assumption 3: (Judge score aggregation)}
A couple's weekly judge score is computed by aggregating all available judge scores for that week. Missing entries are ignored, and invalid values (e.g., non-positive placeholders) are treated as absent rather than informative.

\textbf{Assumption 4: (Fan votes are unobserved)}
Fan votes are not directly observed in the dataset. We treat fan support as a latent (hidden) quantity that influences eliminations together with judges' scores.

\textbf{Assumption 5: (Season-dependent rule regime)}
We assume the show follows different elimination rule regimes across seasons: an early-season ranking-based regime, a mid-season percentage-based regime, and a later-season ``bottom-two with judges' save'' regime. The regime is assumed constant within each season.

\textbf{Assumption 6: (Rule implementation is a faithful proxy)}
When applying elimination rules, we use an operational implementation that matches the intended mechanics:
{\renewcommand{\baselinestretch}{1.0}\selectfont
\begin{itemize}
  \item \texttt{Percent}: combine normalized judges' contribution with fan support and eliminate the lowest combined score.
  \item \texttt{Rank}: combine judges and fan support via rank-based aggregation and eliminate the worst combined rank.
  \item \texttt{Bottom2+JudgeSave}: identify a bottom-two set by combined risk and assume judges save the couple with the higher judges' score.
\end{itemize}
}
We assume this implementation is sufficiently faithful for modeling and comparison purposes, including how ties are handled.

\textbf{Assumption 7: (Week-wise independence)}
Fan support is inferred independently week by week, conditional on that week's active roster and judges' scores. We do not explicitly model temporal dynamics such as popularity momentum across weeks.