\section{Model Evaluation}


\subsection{Advantages}
\begin{itemize}
    \item \textbf{Reproducible pipeline.}
    A modular workflow (Task 1 inference $\rightarrow$ Task 2 replay $\rightarrow$ Task 3 explanation $\rightarrow$ Task 4 design) with all key outputs exported for auditing.

    \item \textbf{Internal validity via replay.}
    Using posterior means $\boldsymbol{\mu}_{s,w}$, the historical-rule replay matches eliminations in $229$ weeks (match rate $1.00$), verifying correct rule implementation.

    \item \textbf{Uncertainty + identifiability diagnostics.}
    Alongside $\mu_{s,w,i}$ we report $\sigma_{s,w,i}$ and week-level signals (\texttt{AvgVoteUncertainty}, acceptance rate $\rho_{s,w}$) to flag hard-to-identify weeks.

    \item \textbf{Stable inference.}
    The three-phase ABC rarely needs relaxation: $228/231$ weeks succeed with exact matching, $3$ use bottom-2 relaxation, none require soft resampling.

    \item \textbf{Actionable counterfactuals and interpretable explanations.}
    Holding fan votes fixed enables clean rule comparisons (flip events, survival shifts $\Delta$). Ridge regressions provide interpretable, regularized feature effects.

    \item \textbf{Transparent rule design with robustness checks.}
    \texttt{FairVote} turns fairness into a tunable trade-off over $(k,\tau)$ and is supported by grid sweeps, bootstrap CIs, and LOSO stability.
\end{itemize}

\subsection{Limitations}
\begin{itemize}
    \item \textbf{Non-identifiability of fan votes.}
    Eliminations are a coarse signal; many vote-share vectors can yield the same eliminated couple, so replay confirms rule-consistency, not uniqueness.

    \item \textbf{Prior and ABC design sensitivity.}
    The posterior depends on $\alpha$ and on relaxation choices (e.g., bottom-2 membership), especially in low-acceptance weeks.

    \item \textbf{Rule simplification risk.}
    The era-based rules approximate broadcast logic; unmodeled special weeks (e.g., double eliminations/withdrawals) may affect comparability.

    \item \textbf{Explanations are correlational.}
    Ridge coefficients capture associations; omitted factors (themes, injuries, narrative effects) can confound interpretation.

    \item \textbf{FairVote trade-offs are explicit, not universally ``fair''.}
    At $(2.0,0.2)$, $\mathbb{P}(\Delta>0)=0.645$, so fan protection is not guaranteed; different objective weights would select different $(k,\tau)$.
\end{itemize}

